---
title: "RWorksheet_Mirabuena#5"
author: "Jessa Mae Mirabuena BSIT 2A"
date: "2022-11-22"
output: pdf_document
---

1. The table shows the enrollment of BS in Computer Science, SY 2010-2011.
Course Year 2019 - 2020
 1st           80
 2nd           75
 3rd           70
 4th           60

a. Plot the data using a bar graph. Write the codes and copy the result.
```{r, include=TRUE}
date2019_2020 <- c(80,75,70,60)
a1a <- barplot(date2019_2020)
```

#b. Using the same table, label the barchart with
#Title = ” Enrollment of BS Computer Science
#horizontal axis = “Curriculum Year” and
#vertical axis = “number of students”
```{r, include=TRUE}
course <- c("1st","2nd","3rd","4th")

a1b <- barplot(date2019_2020,
        main = "Enrollment of BS Computer Science",
        xlab = "Curriculum Year", names.arg = course)
```

2. The monthly income of De Jesus family was spent on the following:
60% on Food, 10% on electricity, 5% for savings, and
25% for other miscellaneous expenses.


a. Create a table for the above scenario.
Write the codes and its result.
```{r, include=TRUE}
expenses <- c(60,10,5,25)

barplot(expenses,names.arg = c("Food", "Electricity", "Savings", "Miscllaneous"))
```

b. Plot the data using a pie chart. Add labels, colors and legend.
Write the codes and its result.
```{r, include=TRUE}
pie(expenses)
b2a <- pie(expenses,
    col = rainbow(length(expenses)),
    labels = c(60,10,5,25))

ex_labels <- round(expenses/sum(expenses) * 100, 1)

ex_labels <- paste(ex_labels,"%",sep = "")
pie(expenses, main = "Expenses",col=rainbow(length(expenses)),labels = ex_labels,cex=0.8)

legend(1, c("Food", "Electricity", "Savings", "Miscllaneous"),
           cex = 0.8,fill = rainbow((length(expenses))))
```
3. Open the mtcars dataset.
```{r, include=TRUE}
data("mtcars")
b3 <- mtcars$mpg
```
a. Create a simple histogram specifically for mpg (miles per gallon) variable.
Use $ to select the mpg only. Write the codes and its result.
```{r, include=TRUE}
b3b <-hist(b3, xlab="Miles Per Gallon",
              main="Histogram of mpg")
```

#b. Colored histogram with different number of bins.
```{r, include=TRUE}
b3c <-hist(b3, breaks=12, col="red", xlab="Miles Per Gallon",
              main="Histogram of mpg")
```
#Note: breaks= controls the number of bins

#c. Add a Normal Curve
```{r, include=TRUE}
numb3c <-hist(b3, breaks=12, col="red", xlab="Miles Per Gallon",
        main="Histogram with Normal Curve")
xfit<-seq(min(b3),max(b3),length=40)
yfit<-dnorm(xfit,mean=mean(b3),sd=sd(b3))
yfit <- yfit*diff(b3c$mids[1:2])*length(b3)
lines(xfit, yfit, col="blue", lwd=2)
```
#Copy the result.


#4. Open the iris dataset. Create a subset for each species.

#a. Write the codes and its result.
```{r, include=TRUE}
data("iris")
set <- subset(iris, Species == "setosa")
ver <- subset(iris, Species == "versicolor")
vir <- subset(iris, Species == "virginica")
```
#b. Get the mean for every characteristics of each species using colMeans().
#Write the codes and its result.
```{r, include=TRUE}
set <- subset(iris, Species == "setosa")
setosa <- colMeans(set[sapply(set,is.numeric)])
setosa

ver <- subset(iris, Species == "versicolor")
versicolor <- colMeans(ver[sapply(ver,is.numeric)])
versicolor

vir <- subset(iris, Species == "virginica")
virginica <- colMeans(vir[sapply(vir,is.numeric)])
virginica
```

#Example: setosa <- colMeans(setosa[sapply(setosaDF,is.numeric)])
#c. Combine all species by using rbind()
#The table should be look like this:
```{r, include=TRUE}
trans3 <- rbind(setosa,
                versicolor,
                virginica)
trans3
```
#Sepal.Length Sepal.Width Petal.Length Petal.Width
#setosa
#versicolor
#virginica


#d. From the data in 4-c: Create the barplot().
#Write the codes and its result.
#The barplot should be like this.
```{r, include=TRUE}
barplot(trans3, beside = TRUE,
        main = "Iris Mean",
        xlab = "Characteristics",
        ylab = "Mean Scores",
        col = c("red","green","blue"))
```
#Figure 1: Iris Data using Barplot
